%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,a4paper,sans]{moderncv}        % options: font size ('10pt', '11pt', '12pt'), paper size ('a4paper', 'letterpaper', etc.), font family ('sans', 'roman')

% moderncv themes
\moderncvstyle{banking}                            % styles: 'casual', 'classic', 'oldstyle', 'banking'
\moderncvcolor{black}                              % colors: 'blue', 'orange', 'green', 'red', 'purple', 'grey', 'black'

% character encoding
\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.95]{geometry}

% packages
\usepackage{enumitem} % for customizing lists

% personal data
\name{Guilherme}{Taschetto}
\title{Tech Lead / Senior Software Engineer}
\address{Canoas, Brazil}{}{}
\phone[mobile]{+55~(51)~99288~3831}
\email{gtaschetto@gmail.com}
\social[linkedin]{taschetto}
\social[github]{taschetto}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}

\makecvtitle

\cvitem{}{I am a seasoned software engineer with extensive experience leading development teams and driving technical initiatives. I am passionate about delivering high-quality, scalable software solutions, while fostering a culture of continuous improvement, collaboration, and alignment with business goals. My experience spans software architecture, cloud infrastructure, and Agile methodologies, with a strong focus on building reliable, high-performance systems.}

\section{Skills}
\cvitem{Leadership}{Team mentoring, Code reviews, Technical guidance, Agile methodologies (Scrum, Kanban), Cross-functional collaboration}
\cvitem{Programming Languages}{Ruby, JavaScript, TypeScript, C, C++, C\#, Python, Java, Progress/OpenEdge}
\cvitem{Web Development}{Ruby on Rails, Node.js, React, Material UI, Vite}
\cvitem{Cloud and DevOps}{AWS (Lambda, S3, CDK, SQS, CloudFront, API Gateway, CloudFormation, ACM, Route 53), Heroku, CI/CD, Infrastructure as Code}
\cvitem{Other}{Test-driven development, Feature flags (LaunchDarkly), Git, Architecture design, System optimization}

\section{Languages}
\cvitemwithcomment{English}{Fluent}{}
\cvitemwithcomment{Portuguese}{Native}{}

\section{Professional Background}
\cventry{2020--\the\year}{Tech Lead / Senior Software Engineer}{Tatango}{Remote}{}{
Led a cross-functional development team in the design and implementation of key features for Tatango's cloud-based SMS/MMS fundraising platform. Responsible for guiding the team's technical decisions and overseeing architecture, with a focus on scalability and high performance. Key accomplishments include:
\begin{itemize}[leftmargin=2em]
    \item Directed the implementation of a Lambda-based processing pipeline capable of handling millions of messages, significantly improving system throughput and reducing latency.
    \item Architected and led the development of a custom URL shortening system capable of processing sudden bursts of millions of redirections to accomodate traffic generated by mass SMS/MMS campaigns.
    \item Streamlined the development process by introducing feature flags, resulting in smaller pull requests and faster development cycles.
    \item Guided the transition from bi-weekly deployments to multiple daily releases, enhancing deployment speed and reducing time-to-market.
    \item Developed an internal CLI tool to automate routine tasks, increasing the team's productivity and reducing manual effort.
    \item Conducted regular code reviews and provided technical mentorship to junior developers, fostering a culture of quality and knowledge sharing.
\end{itemize}
}

\cventry{2018--2020}{Tech Lead / Senior Software Engineer}{eGrid}{Porto Alegre}{}{
Led the development of an electrical energy management SaaS platform, from product inception to delivery. Worked closely with product managers to define requirements and oversee architectural decisions. Key accomplishments include:
\begin{itemize}[leftmargin=2em]
    \item Designed a flexible calculation engine for auditing electric bills from all 27 Brazilian states.
    \item Collaborated with product managers and stakeholders to deliver user-centric reports and dashboards, enhancing data presentation for diverse user levels.
    \item Integrated multiple data sources with the Brazilian free-energy market committee, improving system reliability and interoperability.
    \item Implemented OCR-based automation using AWS Lambda, reducing manual data entry by over 50\%.
    \item Provided technical leadership and mentorship, establishing coding standards and best practices across the team.
\end{itemize}
}

\cventry{2014--2018}{Senior Software Engineer}{Fator 7}{Porto Alegre}{}{
Developed and maintained ERP systems using Ruby on Rails and Progress/OpenEdge. Played a key role in code reviews, mentoring junior developers, and optimizing system architecture for better performance.
}

\cventry{2009--2014}{Software Engineer}{Elipse Software}{Porto Alegre}{}{
Developed communication drivers for industrial protocols and data acquisition systems using C++ and C\#. Provided technical guidance in system integration projects and collaborated with teams on software improvements.
}

\cventry{2003--2008}{Software Engineer}{TOTVS (formerly Datasul)}{Porto Alegre}{}{
Designed and developed custom ERP solutions using Progress/OpenEdge, XHTML, CSS, JavaScript, and Ajax. Responsibilities included database design, technical documentation, and collaboration with clients to meet business needs.
}

\section{Academic Background}
\cventry{2012--2016}{B.Sc. in Computer Science}{PUCRS}{Porto Alegre}{}{}
\cventry{2004--2009}{B.Sc. in Electrical Engineering}{PUCRS}{Porto Alegre}{}{}

\end{document}
